State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-10-23 draft.tex
Minor changes
what happened

[ticket: X]

\section{Problem statement}
%
Throughout this paper we aim to solve the robust model predictive control problem
%
\begin{subequations}\label{seq:general:problem:statement}
\begin{equation}\label{eq:min:max:objective}
  J^\ast_m(x) = \min_u \max_{w,x^+} J(x,u,w) + 
  J^\ast_{m-1}(x^+)
\end{equation}
%
with $J(x,u,w) = \frac{1}{2}\left(x^T Qx + u^TRu - \gamma^2 w^T w\right)$,
%
subject to the system dynamics
%
\begin{equation}\label{eq:system:dynamics}
  x^+ = Ax + Bu + Dw,
\end{equation}
%
the input constraints
%
\begin{equation}\label{eq:general:input:constraints}
  u\in U
\end{equation}
%
\emph{state and input dependent} disturbance constraints
%
\begin{equation}\label{eq:disturbance:constraints}
  w\in\mathcal W(x,u),
\end{equation}
%
and state constraints
%
\begin{equation}\label{eq:general:state:constraints}
  x\in\mathcal X
\end{equation}
\end{subequations}
%
We assume that $Q\geq0$ and $R>0$ are semi-positive and positive definite constant matrices respectively,
the matrices $A,B,D$ are also assumed to be deterministic and known.
%
Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints
like~\eqref{eq:general:state:constraints} can not be robustly satisfied~\cite{Bertsekas:1971}, instead specially designed
ones are used.
%
Recursively defined sets are used to guarantee that the terminal state lies in the 
\emph{maximal robust positive invariant} (MRPI) set~$\mathcal X^\infty\subseteq\mathcal X$ 
(see e.g.~\cite{blanchini:2007}), i.e. the largest set satisfying
%
\begin{equation}\label{eq:definition:MRPI:set}
  \mathcal X^\infty = \{x\in\mathcal X: \Psi x + v \in\mathcal X^\infty\;\forall v\in\mathcal V(x)\}.
\end{equation}
%
The MRPI set~\eqref{eq:definition:MRPI:set} is defined for $\Psi=A+BK$ and $\mathcal V(x) = D\mathcal W(x,Kx)$,
with a fixed feedback controller $u = Kx$.
%
Starting from the MRPI set~$\mathcal X_0=\mathcal X^\infty$ we recursively define
%
\begin{equation}\label{eq:stage:constraints:in:x:and:u}
  \mathcal Z_i = \{(x,u)\in\mathcal X\times U: Ax + Bu + Dw \in\mathcal X_{i-1}\;\forall w\in\mathcal W(x,u)\}
\end{equation}
%
and its projection
%
\begin{equation}
  \mathcal X_i = \{x:\exists u\in U\; (x,u)\in\mathcal Z_i\}.
\end{equation}
%
The state constraint~\eqref{eq:general:state:constraints} and input constraint~\eqref{eq:general:input:constraints}
are then replaced by $(x,u)\in\mathcal Z_m$.
%
To initialise the cost-to-go we use $J_0^\ast(x) = \frac{1}{2}x^T P_0x$, which is designed in combination with the feedback 
controller~$K$ as the optimal unconstrained solution to~\eqref{seq:general:problem:statement}, i.e. they satisfy
$J_0^\ast(x) - J_0^\ast(x^+)\geq J(x,Kx,w)$, see e.g.~\cite{Boyd:94}.
%
The properties of the disturbance constraints~\eqref{eq:disturbance:constraints} will be discussed
in section~\ref{sec:p:convex:sets}.
%
%
%
%
\section{Parametrically Convex Sets}\label{sec:p:convex:sets}
In this section we discuss \emph{parametric convexity}, an attribute of sets valued maps 
(so called point-to-set maps, see e.g.~\cite{Hogan:1973}) we exploit later on to prove 
convexity of a generalised Pontryagin difference in order to 
%
\begin{defi}[Parametric Convexity]\label{def:parametric:convexity}
  Let $X\subseteq\mathbb R^d, Y\subseteq\mathbb R^n$, let $\mathscr P(Y)$ 
  denote the power set of $Y$, 
  and $\mathcal W:X\rightarrow \mathscr P(Y)$, $X\ni p\mapsto \mathcal W(p)
  \subset Y$ be a continuous point-to-set map. The map $\mathcal W$ is called 
  \emph{parametrically convex} if it satisfies
%
  \begin{equation}\label{eq:def:parametrically:convex}
  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2)
  \end{equation}
%
  for all $p_1,p_2\in X$ and $\lambda\in[0,1]$.
\end{defi}
%
Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$ for all
$p\in X$, we will however only treat maps~$\mathcal W$ for which $\mathcal W(p)$ is convex.

@@

$\mathcal W(x)$ defined by~\eqref{eq:definition:PWA:polytopic:set:general}. 

@@

  \bar\sigma({\bf{c}})\norm{x}+\norm{{\bf{b}}}
  \geq\bar\sigma({\bf{c}}_{k^\ast})\norm{x}+\norm{{\bf{b}}_{k^\ast}}\\
  =\max_k\{\bar\sigma({\bf{c}}_k)\norm{x}+\norm{{\bf{b}}_k}\}
  \geq\norm{\max_k\{{\bf{c}}_{\mathscr{A}_i,k} x + {\bf{b}}_{{\mathscr{A}_i},k}\}}\\ 
  =\norm{{\bf{a}}_{\mathscr{A}_i}v_i} \geq\underline\sigma({\bf{a}}_{\mathscr A_i})\norm{v_i}
  \geq\underline\sigma({\bf{a}})\norm{v_i}.

@@

@@

exact bounds on intermediate iterates, hence $r_2\leq\frac{\bar\sigma({\bf{c}})r_3+\norm{{\bf{b}}}}
{\underline\sigma({\bf{a}})}$ can be used as an estimate for the asymptotic behaviour of $\mathcal V(x)$

>>>>

\section{Problem statement}
Throughout this paper we aim to solve the robust model predictive control problem
\begin{subequations}\label{seq:general:problem:statement}
\begin{equation}\label{eq:min:max:objective}
  J^\ast_m(x) = \min_u \max_{w,x^+} J(x,u,w) + 
  J^\ast_{m-1}(x^+)
with $J(x,u,w) = \frac{1}{2}\left(x^T Qx + u^TRu - \gamma^2 w^T w\right)$,
subject to the system dynamics
\begin{equation}\label{eq:system:dynamics}
  x^+ = Ax + Bu + Dw,
the input constraints
\begin{equation}\label{eq:general:input:constraints}
  u\in U
\emph{state and input dependent} disturbance constraints
\begin{equation}\label{eq:disturbance:constraints}
  w\in\mathcal W(x,u),
and state constraints
\begin{equation}\label{eq:general:state:constraints}
  x\in\mathcal X
We assume that $Q\geq0$ and $R>0$ are semi-positive and positive definite constant matrices respectively,
the matrices $A,B,D$ are also assumed to be deterministic and known.
Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints
like~\eqref{eq:general:state:constraints} can not be robustly satisfied~\cite{Bertsekas:1971}, instead specially designed
ones are used.
Recursively defined sets are used to guarantee that the terminal state lies in the 
\emph{maximal robust positive invariant} (MRPI) set~$\mathcal X^\infty\subseteq\mathcal X$ 
(see e.g.~\cite{blanchini:2007}), i.e. the largest set satisfying
\begin{equation}\label{eq:definition:MRPI:set}
  \mathcal X^\infty = \{x\in\mathcal X: \Psi x + v \in\mathcal X^\infty\;\forall v\in\mathcal V(x)\}.
The MRPI set~\eqref{eq:definition:MRPI:set} is defined for $\Psi=A+BK$ and $\mathcal V(x) = D\mathcal W(x,Kx)$,
with a fixed feedback controller $u = Kx$.
Starting from the MRPI set~$\mathcal X_0=\mathcal X^\infty$ we recursively define
\begin{equation}\label{eq:stage:constraints:in:x:and:u}
  \mathcal Z_i = \{(x,u)\in\mathcal X\times U: Ax + Bu + Dw \in\mathcal X_{i-1}\;\forall w\in\mathcal W(x,u)\}
and its projection
  \mathcal X_i = \{x:\exists u\in U\; (x,u)\in\mathcal Z_i\}.
The state constraint~\eqref{eq:general:state:constraints} and input constraint~\eqref{eq:general:input:constraints}
are then replaced by $(x,u)\in\mathcal Z_m$.
To initialise the cost-to-go we use $J_0^\ast(x) = \frac{1}{2}x^T P_0x$, which is designed in combination with the feedback 
controller~$K$ as the optimal unconstrained solution to~\eqref{seq:general:problem:statement}, i.e. they satisfy
$J_0^\ast(x) - J_0^\ast(x^+)\geq J(x,Kx,w)$, see e.g.~\cite{Boyd:94}.
Both input and state constraint sets are assumed polyhedral $U=\{u:F_iu\leq1\forall i\in\mathcal I_U\}$ and $\mathcal X = 
\{x:\genmat_i x\leq \genvec_i\forall i\in\mathcal I_{\mathcal X}\}$.
For the disturbance set~\eqref{eq:disturbance:constraints} we assume that there exists a piecewise affine representation
\begin{equation}\label{eq:definition:disturbance:set:explicit}
  \mathcal W(x,u) = \{w:G_i w\leq\max_{k}\{H_{i,k}^x x + H_{i,k}^u + h_{i,k}\}\forall i\in\mathcal I_{\mathcal W}\}.
The properties of such sets will be discussed in section~\ref{sec:p:convex:sets}.
\section{Parametrically Convex Sets}\label{sec:p:convex:sets}
In this section we discuss \emph{parametric convexity}, an attribute of sets valued maps 
(so called point-to-set maps, see e.g.~\cite{Hogan:1973}) we exploit later on to prove 
convexity of a generalised Pontryagin difference in order to 
\begin{defi}[Parametric Convexity]\label{def:parametric:convexity}
  Let $X\subseteq\mathbb R^d, Y\subseteq\mathbb R^n$, let $\mathscr P(Y)$ 
  denote the power set of $Y$, 
  and $\mathcal W:X\rightarrow \mathscr P(Y)$, $X\ni p\mapsto \mathcal W(p)
  \subset Y$ be a continuous point-to-set map. The map $\mathcal W$ is called 
  \emph{parametrically convex} if it satisfies
  \begin{equation}\label{eq:def:parametrically:convex}
  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2)
  for all $p_1,p_2\in X$ and $\lambda\in[0,1]$.
Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$ for all
$p\in X$, we will however only treat maps~$\mathcal W$ for which $\mathcal W(p)$ is convex.

@@

$\mathcal W(x)$ defined by~\eqref{eq:definition:disturbance:set:explicit}. 

@@

  \bar\sigma(\bar{\bf{H}})\norm{x}+\norm{{\bf{h}}}
  \geq\bar\sigma(\bar{\bf{H}}_{k^\ast})\norm{x}+\norm{{\bf{h}}_{k^\ast}}\\
  =\max_k\{\bar\sigma(\bar{\bf{H}}_k)\norm{x}+\norm{{\bf{h}}_k}\}
  \geq\norm{\max_k\{\bar{\bf{H}}_{\mathscr{A}_i,k} x + {\bf{h}}_{{\mathscr{A}_i},k}\}}\\ 
  =\norm{{\bf{G}}_{\mathscr{A}_i}v_i} \geq\underline\sigma({\bf{G}}_{\mathscr A_i})\norm{v_i}
  \geq\underline\sigma({\bf{G}})\norm{v_i}.

@@

with $\bar{\bf{H}} = ({\bf{H}}^x + {\bf{H}}^u K)$.

@@

exact bounds on intermediate iterates, hence $r_2\leq\frac{\bar\sigma(\bar{\bf{H}})r_3+\norm{{\bf{h}}}}
{\underline\sigma({\bf{G}})}$ can be used as an estimate for the asymptotic behaviour of $\mathcal V(x)$
